\LARGE \bf \acro: Reducing Supervisor Burden using SVM-based Risk to Efficiently Learn Robot Control Policies from Demonstrations {\color{blue}(v.10)}

### 2015-08-08 paper.tex
Updates from ShareLaTeX

\author{Michael Laskey$^1$,Wesley Yu-Shu Hsieh, Jeff Mahler, Florian T. Pokorny$^1$, Ken Goldberg$^2$% <-this % stops a space
\thanks{$^1$Department of Electrical Engineering and Computer Sciences; {\small \{mdlaskey, ftpokorny\}@berkeley.edu}}%
\thanks{$^2$Department of Industrial Engineering and Operations Research and Department of Electrical Engineering and Computer Sciences; {\small goldberg@berkeley.edu}}%
\thanks{$^{1-2}$ University of California, Berkeley;  Berkeley, CA 94720, USA}%
}

@@

\begin{abstract}
For robot control problems where no reward function is known and the dynamics of the environment are not specified, the
learning from demonstrations approach provides an algorithmic paradigm for learning a policy from supervisor-provided
demonstrations. Dataset Aggregation (DAgger) in particular yields a state of the art method in this context which treats
the problem of determining a policy as an iterative supervised learning problem. DAgger alternates between executing a
trained policy and acquiring new supervisor control inputs for roll-outs of a current best policy estimator. 
We propose a novel algorithm, \acro~ based on DAgger which estimates the riskiness of states
encountered by the policy roll-outs by means of an approximate quantile super-levelset estimate of the distribution of
states used for training the current policy and which additionally takes empirical surrogate loss of the current policy
into account. Since learning a quantile function for high-dimensional input data is
challenging, we instead modify an SVN-based approach to quantile estimation that employs regularization to solve this
problem approximately. Our algorithm considers roll-outs with early termination as soon as a state outside a
user-defined quantile super-levelset is encountered. Our approach empirically reduces the amount of neccessary
supervisor demonstrations by only collecting supervisor control inputs at states outside the current quantile estimate.
In experiments involving a simulated race track and in a Super Mario Atari game benchmark considered by the authors of
DAgger, our approach results in similar peak performance levels as DAgger while reducing the amount of required supervisor
control inputs by more than {\color{blue}[-- TODO --]} percent.
\end{abstract}

>>>>

\author{Michael Laskey$^1$,Wesley Yu-Shu Hsieh, Jeff Mahler, Florian T. Pokorny$^1$, Anca Dragan, Ken Goldberg$^2$% <-this % stops a space
\thanks{$^1$Department of Electrical Engineering and Computer Sciences; {\small \{mdlaskey, ftpokorny\}@berkeley.edu}}%
\thanks{$^2$Department of Industrial Engineering and Operations Research and Department of Electrical Engineering and Computer Sciences; {\small goldberg@berkeley.edu}}%
\thanks{$^{1-2}$ University of California, Berkeley;  Berkeley, CA 94720, USA}%
}

@@

\begin{abstract}
For robot control problems where no reward function is known and the dynamics of the environment are not specified, the
learning from demonstrations approach provides an algorithmic paradigm for learning a policy from supervisor-provided
demonstrations. Dataset Aggregation (DAgger) in particular yields a state of the art method in this context which treats
the problem of determining a policy as an iterative supervised learning problem. DAgger alternates between executing a
trained policy and acquiring new supervisor control inputs for roll-outs of a current best policy estimator. 
We propose a novel algorithm, \acro~ based on DAgger which estimates the riskiness of states
encountered by the policy roll-outs by means of an approximate quantile super-levelset estimate of the distribution of
states used for training the current policy and which additionally takes empirical surrogate loss of the current policy
into account. Since learning a quantile function for high-dimensional input data is
challenging, we instead modify an SVM-based approach to quantile estimation that employs regularization to solve this
problem approximately. Our algorithm considers roll-outs with early termination as soon as a state outside a
user-defined quantile super-levelset is encountered. Our approach empirically reduces the amount of neccessary
supervisor demonstrations by only collecting supervisor control inputs at states outside the current quantile estimate.
In experiments involving a simulated race track and in a Super Mario Atari game benchmark considered by the authors of
DAgger, our approach results in similar peak performance levels as DAgger while reducing the amount of required supervisor
control inputs by more than {\color{blue}[-- TODO --]} percent.
\end{abstract}
